agdarsec -- Total Parser Combinators

### 2017-10-27 doc/paper/main.tex
[ doc ] hchainl

The typical solution to this problem is to introduce two 'tiers'
of expressions: the \parser{base} ones which can only be whole
expressions if we consume an opening parenthesis first and the
\parser{expr'} ones which are left-associated chains of \parser{base}
expressions connected by '+'.

@@

\subsection{Left and Right Chains}

@@

We define \parser{schainl} as the fixpoint of either \parser{rest}
(whose definition we omit here) or the \AR{Success} that was passed
as an input (the function \AF{\_::$^{r}$} appends a single element
at the end of a list).

@@

>>>>

The typical solution to this problem is to introduce two 'tiers'
of expressions: the \parser{base} ones which can only be whole
expressions if we consume an opening parenthesis first and the
\parser{expr'} ones which are left-associated chains of \parser{base}
expressions connected by '+'.\label{parser:expr}

@@

\section{Left and Right Chains}

@@

We define \AF{schainl} as the fixpoint of either \AF{rest} (whose
definition we omit here) or the \AR{Success} that was passed as an
input (the function \AF{\_::$^{r}$} appends a single element at the
end of a list).

@@

From this definition we can derive \AF{iterate} which takes a parser for
a seed and a parser for a function and kickstarts a call to \AF{schainl}
on the result of the parser for the seed.

\agrab{Text/Parser/Combinators}{iterate}

Finally, \AF{hchainl} can be implemented using \AF{iterate}, the applicative
structure of \AR{Parser} and some of the properties of \BOX{}.

\agrab{Text/Parser/Combinators}{hchainl}

As we have mentioned when defining \AF{schainl}, the combinator \AF{hchainl}
we have just implemented does not expect fully-defined parsers as arguments.
As a consequence it can be used inside a fixpoint construction. Both the parser
for the constructor and the one for its \AB{B} argument are guarded whilst the
one for the \AB{A} seed is not. This means that trying to define a left-recursive
grammar by immediately using a recursive substructure on the left is now a type
error. But it still possible to have some on the right or after having consumed
at least one character (typically an opening parenthesis, cf. the \type{Expr}
example in Section~\ref{parser:expr}).
